%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\bibitem{1} Lin, Y., Hwang, R. and Baker, F. (2012). Computer networks. New York, NY: McGraw-Hill. 

\bibitem{2} B. Forouzan, Data communications and networking. New York: MacGraw-Hill, 2013.

\bibitem{3} "Here's how a tiny Pacific island got better Internet than the US", Public Radio International, 2018. [Online]. Available: https://www.pri.org/stories/2014-08-01/heres-how-tiny-pacific-island-got-better-internet-us. [Accessed: 21- Mar- 2018].

\bibitem{4} U. Speidel, E. Cocker, P. Vingelmann, J. Heide and M. Medard, "Can network coding bridge the digital divide in the pacific?", 2015 International Symposium on Network Coding (NetCod), 2015.

\bibitem{5} U. Speidel, L. Qian, ’. Cocker, P. Vingelmann, J. Heide and M. Médard, "Can Network Coding Mitigate TCP-induced Queue Oscillation on Narrowband Satellite Links?", Wireless and Satellite Systems, pp. 301-314, 2015.

\bibitem{6} Border J, Kojo M, Griner J, Montenegro G, Shelby Z. “Performance Enhancing Proxies Intended to Mitigate Link-Related Degradations”, IETF RFC 3135, June 2001.

\bibitem{7} Y. Hu and V. Li, “Satellite-based internet: a tutorial”, IEEE Commun. Mag., pp. 154-62, March. 2001.

\bibitem{8} C Partridge, T Shepard, "TCP Performance over Satellite Links", IEEE Network, vol. II, no. 5, pp. 44, September 1997.

\bibitem{9} G. Xylomenos, G.C. Polyzos, P., Mahonen, and M. Saaranen, “TCP performance issues over wireless links” IEEE Commun.Mag., vol. 39, pp 52-58, April 2001.

\bibitem{10} M. Marchese, “TCP/IP-Based Protocols Over Satellite Systems: A Telecommunication Issue,” in Reliability, Survivability and Quality of Large Scale Telecommunication Systems, P. Stavroulakis, Ed. Chichester: Wiley, 2003, pp. 167-198.

\bibitem{11} K. Scott, P. Feighery, B. Crow and M. Jurik, “TCP congestion control in shared satellite environments”, MILCOM 2002 - IEEE Military Communications Conference, no. 1, October 2002, pp. 46 – 50.  

\bibitem{12} D. E. Comer, Internetworking with TCP/IP, Vol. I: Principles, Protocols and Architecture, 2nd ed., Prentice Hall, 1991. 

\bibitem{13} Partridge, C. and Shepard, T. (1997). TCP/IP performance over satellite links. IEEE Network, 11(5), pp.44-49.

\bibitem{14} Caini, C., Firrincieli, R. and Lacamera, D. (2007). PEPsal: A Performance Enhancing Proxy for TCP Satellite Connections [Internetworking and Resource Management in Satellite Systems Series]. IEEE Aerospace and Electronic Systems Magazine, 22(8), pp.B9-B16.

\bibitem{15}  Thanthry, N., Deshpande, M. and Pendse, R. (2006). A Novel Mechanism for Improving Performance and Security of TCP Flows over Satellite Links. Proceedings 40th Annual 2006 International Carnahan Conference on Security Technology.

\bibitem{16} M. Allman et. al., " Ongoing TCP Research Related to Satellites", RFC 2760, February 2000 

\bibitem{17} Allman M, Blanton E, Paxson V. “TCP Congestion Control”, IETF RFC 5681, September 2009. 

\bibitem{18} Stevens W. “TCP Slow Start, Congestion Avoidance, Fast Retransmit, and Fast Recovery Algorithms”, IETF RFC 2001, January 2001. 

\bibitem{19} V. Jacobson, "Congestion avoidance and control", ACM SIGCOMM Computer Communication Review, vol. 25, no. 1, pp. 157-187, 1995. 

\bibitem{20} U. Speidel, "Striking a balance between bufferbloat and TCP queue oscillation | APNIC Blog", APNIC Blog, 2018. [Online]. Available: https://blog.apnic.net/2018/03/19/striking-a-balance-between-bufferbloat-and-tcp-queue-oscillation/. [Accessed: 20- Mar- 2018].

\bibitem{21} "Auckland Satellite TCP/IP Traffic Simulator | Home of the Satellite TCP/IP Traffic Simulator at the University of Auckland", Sde.blogs.auckland.ac.nz, 2018. [Online]. Available: http://sde.blogs.auckland.ac.nz/. [Accessed: 25- Mar- 2018].

\bibitem{22} Z. Liu eta/., "Evaluation of TCP Vegas: Emulation and Experiment," Proc. ACM SIGCOMM '95, Aug. 1995, pp. 185-1 96.

\bibitem{23} J. C. Hoe, "Improving the Start-up Behavior of a Congestion Control Scheme for TCP," Proc. ACM SIGCOMM '97, Aug. 1996, p 270-280 

\bibitem{24} M. Mathis and J. Mahdavi, "Forward Acknowledgment: Refining TCP Congestion Control," Proc. ACM SIGCOMM '96, Aug. 1996, pp. 281-291.

\bibitem{25} L. S. Brakmo, S. W. OMalley, and L. L. Peterson, "TCP Vegas: New Techniques for Congestion Avoidance and Control," Proc. ACM SIGCOMM '94,
Aug. 1994, pp. 24-35.

\bibitem{26} C. Caini and R. Firrincieli, “TCP Hybla: a TCP Enhancement for Heterogeneous Networks”, International Journal of Satellite Communications and Networking, vol. 22, n. 5, Sep. 2004, pp. 547-566.

\bibitem{27} C. E. Palazzi, C. Roseti, M. Luglio, M. Gerla, M. Y. Sanadidi, and J. Stepanek, “Enhancing Transport Layer Capability in HAPS-Satellite Integrated Architecture”, Wireless Personal Communications, Springer Science+Business Media B.V. (formerly Kluwer Academic Publishers B.V.), vol. 32, no. 3-4, Feb 2005. 

\bibitem{28} D. Velenis, D. Kalogeras, and B. Maglaris, “SaTPEP: a TCP Performance Enhancing Proxy for Satellite Links,” 2nd International IFIPTC6 Networking Conference, May 2002. 

\bibitem{29} "US6975647B2 - Enhancements for TCP performance enhancing proxies - Google Patents", Patents.google.com, 2018. [Online]. Available: https://patents.google.com/patent/US6975647B2/en. [Accessed: 25- Mar- 2018].

\bibitem{30} A. Bakre, B. R. Badrinath, “I-TCP: Indirect TCP for Mobile Hosts”, Proc. 15th IEEE International Conference on Distributed Computing Systems, Vancouver, British Columbia, pp. 136-143, May 1995. 

\bibitem{31} R. Yavatkar and N. Bhagawat, “Improving end-to-end performance of TCP over mobile internetworks”. IEEE Workshop on Mobile Computing Systems and Applications, pages 146--152, December 1994. 

\bibitem{32} T.R. Henderson, and R.H. Katz, “Satellite Transport Protocol (STP): An SSCOP-based Transport Protocol for Datagram Satellite Networks”, 2nd International Workshop on Satellite-based Information Services (WOSBIS `97), Budapest, Hungary, Oct. 1, 1997. 

\bibitem{33} "GregoireDelannoy/TCPeP", GitHub, 2018. [Online]. Available: https://github.com/GregoireDelannoy/TCPeP. [Accessed: 25- Mar- 2018]. 

\bibitem{34} Artes.esa.int, 2018. [Online]. Available: https://artes.esa.int/sites/default/files/FastSatDataSheet\textunderscore 1.5.pdf. [Accessed: 25- Mar- 2018]. 

\bibitem{35} S. Walton, Linux socket programming. Indianapolis]: Sams, 2008. 

\bibitem{36} "packet(7) - Linux manual page", Man7.org, 2018. [Online]. Available: http://man7.org/linux/man-pages/man7/packet.7.html. [Accessed: 26- Mar- 2018]. 

\bibitem{37} "IBM Knowledge Center Error", Ibm.com, 2018. [Online]. Available:https://www.ibm.com/support/knowledgecenter/en/SSLTBW\textunderscore 2.3.0/com.ibm.zos.v2r3.cbcpx01/ovsock.htm. [Accessed: 26- Mar- 2018].

\bibitem{38} A. Sockets and S. Saxena, "A Guide to Using Raw Sockets", Open Source For You, 2018. [Online]. Available: http://opensourceforu.com/2015/03/a-guide-to-using-raw-sockets/. [Accessed: 26- Mar- 2018]. 

\bibitem{39} B. Kernighan and D. Ritchie, The C programming language. Englewood Cliffs, N.J.: Prentice-Hall, 2011.

\bibitem{40} "netdevice(7) - Linux manual page", Man7.org, 2018. [Online]. Available: http://man7.org/linux/man-pages/man7/netdevice.7.html. [Accessed: 26- Mar- 2018].

\bibitem{41} D. E. Comer, Internetworking with TCP//P, Vol. I: Principles, Protocols and Architecture, 2nd ed., Prentice Hall, 1991. 

\bibitem{42}  Bentley, "Multidimensional binary search trees used for associative searching", Communications of the ACM, vol. 18, no. 9, pp. 509-517, 1975. 

\bibitem{43} A. Aho, J. Hopcroft and J. Ullman, Data Structures and algorithms. Delhi: Dorling Kindersly, 2009. 

\bibitem{44} "packet(7) - Linux manual page", Man7.org, 2018. [Online]. Available: http://man7.org/linux/man-pages/man7/packet.7.html. [Accessed: 02- Apr- 2018].


